\addcontentsline{toc}{chapter}{Acknowledgements}
\begin{center}
\textbf{\large Acknowledgements}
\end{center}

First and foremost, I'd like to give my thanks to my advisor, Gordon Cates, for supporting me in the past five years in the group. Not only because I have learned a lot about physics from you, but also for your incredible enthusiasm that kept motivating me to push towards earning my degree. I am honored to have worked with you.

I'd like to thank Peter Dolph and Yuan Zheng, who have taught me the basics of spin-exchange optical pumping and $^3$He and alkali polarimetry. Even though the time we spent working together was not long, it laid the very foundation for my work in the following years.

I would like to thank Dr. W. Al Tobias and Dr. Vladimir Nelyubin as well. Al has helped us fill almost every cell we have studied and also taught me the right way to do experiments and the importance of documentation. Vladimir always made sure our experiments could go as smoothly as possible with his laser expertise. We would not have been able to do it without the help from Al and Vladimir.

I also would like to thank all the other graduate students in the group. Maduka Kaluarachchi and Dan Matyas, the two of you made the hours in lab such a joy. I will always miss our talks and of course, the "Young Chicken" we shared at Taste of China. Graduate school was not an easy time for me, I could not have done it without the help from you guys. Sumudu Katugampola and Dave Keder, the two of you are already doing great work, I have no doubt that you will have tremendous amount of success in the future. I look forward to seeing what our lab will be able to achieve because of you.

I'd like to thank the members of my committee: Nilanga Liyanage, Don Crabb, Wilson Miller, for helping me complete the final step towards my degree. I also owe my thanks to my parents and all my friends who have supported me through all these years. It means a lot to me knowing that no matter what comes next, I will always have your support.

Last but not least, I would like to thank my girlfriend. Shuangshuang, every bit of success I was able to achieve since I met you was at least partly because of your love and support. You gave me something to hold on to so I could pull myself through a tough time. I would not have been able to move on to the next chapter of my life the same way I did without you.



%\vspace{1cm}

%\emph{``Intellectual and practical assistance, advice, encouragement and
%sources of monetary support should be acknowledged. It is appropriate to
%acknowledge the prior publication of any material included in the thesis
%either in this section or in the introductory chapter of the thesis.''}

%\hfill --- MUN School of Graduate Studies
