\chapter{$^{3}$He Polarimetry}
\label{chap:chap3}

\section{Overview}

Traditional pure glass target cells are studied mainly using Adiabatic Fast Passage (AFP) Nuclear Magnetic Resonance (NMR) and Electron Paramagnetic Resonance (EPR). AFP is a technique that allows us to monitor a signal that's directly proportional to the ${3}He$ polarization, which then provides a means to gain knowledge of properties of cell including pumping time and relaxation rates. The EPR technique utilizes the fact that polarized $^{3}$He produces frequency shift of the magnetic resonance lines of alkali metal to measure the $^{3}$He polarization. When AFP and EPR are combined, we can calculate the calibration constant between AFP signal and $^{3}$He polarization. 

A significant focus of my studies is on exploring cells that incorporate metal. Unfortunately, AFP is not suitable for studying these cells as it requires exposing the entirety of the cell to a Radio Frequency magnetic field in an attempt to flip all spins in the cell. For these cells, Pulsed Nuclear Magnetic Resonance (PNMR) has proven to be very useful. PNMR only applies a pulsed RF field to a small selected part of the cell which makes it relatively easy to prevent metal from distorting the signal. However, the spins tipped by applying the pulse lose their transverse component (which depends on the "tip angle"), we typically allow some time for this portion of gas to diffuse out of the region before taking the next measurement on a fresh sample of the gas. The rate at which measurements are taken is limited by this requirement.

This chapter introduces the three techniques mentioned above and how they're used for our studies.

\section{Adiabatic Fast Passage}

\subsection{Nuclear Magnetic Resonance}

The energy of a magnetic moment in an external field is

\begin{equation}
E = -\vec{\mu}\cdot \vec{B_{0}} = -\mu_{z}B_{0}
\end{equation}

where $\vec{\mu}$ is the magnetic moment, for a spin-1/2 nuclei, the energy is

\begin{equation}
E = -\gamma B_{0}\hbar/2
\end{equation}

$\gamma$ is the gyromagnetic ratio, $\gamma /2\pi \approx 3.2434kHz/Gauss$. When a oscillating magnetic field with the frequency $\omega=\gamma B_{0}$ is present, transitions between the +1/2 and -1/2 states are induced. This frequency is called Larmor frequency. When a nucleus is placed in an external magnetic field that is not aligned with its magnetic moment, it will precess at the Larmor frequency.

\subsection{The Rotating Coordinate System}

\subsubsection{Classical Formulation}

For a nucleus in an external field $\vec{B}$ with $\gamma \hbar \vec{I}$ as its nuclear angular momentum, the equation of motion in a stationary coordinate system is \cite{RevModPhys.26.167}

\begin{equation}\label{eq1}
\hbar \frac{d\vec{I}}{dt}=\gamma \hbar \vec{I} \times \vec{B}
\end{equation}

Let $\frac{\partial}{\partial t}$ represent the derivative with respect to a coordinate system that rotates with angular velocity $\vec{\omega}$,

\begin{equation}{eq2}
\frac{d\vec{I}}{dt}=\frac{\partial \vec{I}}{\partial t}+\vec{\omega} \times \vec{I}
\end{equation}

Substitute Eq.\ref{eq2} into Eq.\ref{1}, $\vec{I}$ in the rotating frame satisfies the equation of motion 

\begin{equation}
\hbar \frac{\partial \vec{I}}{\partial t}=\gamma \hbar \vec{I} \times (\vec{B} + \vec{\omega}/\gamma)=\gamma \hbar \vec{I} \times \vec{B_{eff}}
\end{equation}

where $\vec{B_{eff}}$ is the effective field in the rotating frame

\begin{equation}
\vec{B_{eff}}=\vec{B} + \vec{\omega}/\gamma
\end{equation}

Thus, for an observer in the rotating frame, the net effect is the same as changing the field to include an additional term $\omega/\gamma$.

If we apply this result to rotating magnetic fields, we will get the core idea of performing an Adiabatic Fast Passage (AFP) measurement. Assuming a constant field $\vec{B}$ and another field $\vec{B_{1}}$ perpendicular to $\vec{B}$ and rotates with angular velocity $-\omega$. In the rotating frame that rotates with $\vec{B_{1}}$, both aforementioned field are constant. The effective field in the rotating frame is

\begin{equation}\label{EffectiveField}
B_{eff}\vec{z}=(B-\omega/\gamma)\vec{z} + B_{1}\vec{x'}
\end{equation}

where $\vec{x'}$ is the direction that $\vec{B_{1}}$ is in. When on resonance (B = $\omega/\gamma$), the effective field is perpendicular to the constant field $\vec{B}$.

\subsubsection{Quantum Mechanical Formulation}

The Shr$\ddot{o}$dinger equation for a magnetic moment in an external field is

\begin{equation}\label{eq3}
i\hbar \dot{\psi}=\mathcal{H} \psi=-\gamma \hbar \vec{I}\cdot \vec{B} \psi
\end{equation}

Let $\psi$ and $\vec{B}$ be the wave function and magnetic field in a stationary frame and $\psi_{r}$ and $\vec{B_{r}}$ be the same quantities in a rotating frame with angular velocity $\vec{\omega}$. Using the rotation operator in quantum mechanics, 

\begin{subequations}\label{eq4}
	\begin{gather}
	\psi=e^{-i\vec{\omega}\cdot \vec{I}t}\psi_{r} \\
	\vec{I}\cdot \vec{B_{r}} = e^{i\vec{\omega}\cdot \vec{I}t}\vec{I}\cdot \vec{B} e^{-i\vec{\omega}\cdot \vec{I}t}
	\end{gather}
\end{subequations}

Substituting \ref{eq3} into Eq.\ref{eq3}, the Shr$\ddot{o}$dinger equation in the rotating frame is obtained

\begin{equation}
i\hbar \dot{\psi_{r}}=-\gamma \hbar \vec{I}\cdot(\vec{B_{r}} + \vec{\omega}/\gamma)\psi_{r}=-\gamma \hbar \vec{I}\cdot\vec{B_{eff}}\psi_{r}
\end{equation}

The same effective field in the rotating frame is reached as that from the classical derivation.

\subsection{Adiabatic Fast Passage}

Adiabatic Fast Passage (AFP) NMR is used to measure the $^{e}$He polarization. In an AFP measurement, with the assistance of a oscillating radiofrequency (RF) field, the spins follow the effective field in a rotating frame (as discussed in more detail below) and are flipped 180 degrees to the opposite direction and then flipped back, producing two peaks in signal when they're perpendicular to the pick up coils.

The flipping process can be achieved by either sweeping the main holding field or sweeping the RF frequency so that the longitudinal component of effective field in the rotating field goes through zero. AFP measurements in out lab are typically done by sweeping the holding field while keeping the RF frequency constant. The RF coils produce a RF field of magnitude 2$B_{1}$ perpendicular to the main holding field B. The oscillating field has a frequency of $\omega$ and can be decomposed into two counter-rotating components with the same amplitude B$_{1}$. Only the component rotating in direction to be able to give a resonance in Eq.\ref{EffectiveField} has an important effect. In this frame, the effective field is

\begin{equation}
B_{eff}\vec{z}=(B-\omega/\gamma)\vec{z} + B_{1}\vec{x'}
\end{equation}

as discussed above. The other rotating component does not affect the spins. In an AFP measurement, the holding field starts from a value that's lower than $\omega/\gamma$ ($\omega/\gamma-B\gg B_{1}$), so that the effective field is almost aligned with the holding field (and the spins). The holding field is then swept at a constant rate through resonance to a value greater than $\omega/\gamma$. The sweeping rate is of great importance. The sweep needs to be slow enough so that the nuclear spins can follow the effective field

\begin{equation}
\frac{\dot B}{B_{1}}\ll \omega
\end{equation}

Sweep that satisfies this condition is considered as adiabatic.










